I can see clearly now: reinterpreting statistical significance

### 2019-01-06 doc.tex
Last version with dmu

The value of NHST can be seen in something like a permutation-based t-test \cite[Chapter 1]{GoodBook}: it provides a simple, robust framework to ask whether we can tell \emph{which} mean is bigger. More generally, testing the null hypothesis is a proxy for asking whether we clearly see a signal of how our data differs from it. In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \citep{robinson2001past}. In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether an effect has been seen clearly.

>>>>

The value of NHST is that asking whether we can reject the null hypothesis is a proxy for asking whether we clearly \emph{how} our data differs from it. For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we a confident which of the two means is \emph{larger}; similarly, tests for whether two values are correlated are a proxy for whether we can see the sign of the correlation coefficient \citep{robinson2001past}. In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference we see, but NHST is still a reasonable, accepted way to evaluate whether an effect has been seen clearly.
